Detecting distributional differences between temporal granularities for exploratory time series analysis

### 2021-05-25 paper/main.Rmd
down to 30 pages (need to remove figs)

- _Modelling approach:_  $wpd_{raw}$ being a Jensen-Shannon distance, follows a Chi-square distribution (@JSD), which is a special case of Gamma distribution. Hence, a Gamma generalized linear model (GLM) for $wpd_{raw}$ is fitted with number of comparisons as the explanatory variable, which is of the following form:

>>>>

- _Modeling approach:_  $wpd_{raw}$ being a Jensen-Shannon distance, follows a Chi-square distribution (@JSD), which is a special case of Gamma distribution. Hence, a Gamma generalized linear model (GLM) for $wpd_{raw}$ is fitted with number of comparisons as the explanatory variable, which is of the following form:
